---
title: "Introduction to seoulsubway"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to seoulsubway}
  \usepackage[utf8]{inputenc}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
options(tibble.print_min = 4L, tibble.print_max = 4L)
library(seoulsubway)
```

This document introduces you to seoulsubway's basic set of tools, and shows you how to apply them to sample data("subway_sample").


## Data: subway_sample

```{r}
data("subway_sample")
dim(subway_sample)
head(subway_sample)
```
Note that `subway_sample` is a data.table and data.frame. It contains 5000 obs(path sample) and 7 variables. 

Seven variables include riding station, riding line, getting off station, getting off line, time, and number of passengers.

## Introduction to functions.

* `shortestpath()` will give you information about the shortest path to the subway.

* `shortestpath_0()` will give you information about the shortest path to the subway when you don't transfer.

* `shortestpath_1()` will give you information about the shortest path to the subway when you do transfer only one time.

* `shortestpath_2()` will give you information about the shortest path to the subway when you do transfer only two time.

* `pathplot()` will give you map which include shortestpath informataion. 


## Find path for sample data

### Find shortestpath for zero transfer count

when you input arrival_line == depart_line path route.

`shortestpath_0` will give you information about the shortest path to the subway when you don't transfer. also It considered circulate line #2

```{r}
samplepath <- subway_sample[which(subway_sample$ID=="ID124"),]
samplepath
shortestpath_0(depart = samplepath$up_Name, depart_line = samplepath$up_Line,
             arrival = samplepath$down_Name, arrival_line = samplepath$down_Line)
```

### Find shortestpath for one transfer count

`shortestpath_1` will give you information about the shortest path to the subway when you do only one transfer. 

```{r}
samplepath <- subway_sample[which(subway_sample$ID=="ID142"),]
samplepath
shortestpath_1(depart = samplepath$up_Name, depart_line = samplepath$up_Line,
             arrival = samplepath$down_Name, arrival_line = samplepath$down_Line)
```


### Find shortestpath for two transfer count

`shortestpath_2` will give you information about the shortest path to the subway when you do two transfer.

```{r}
samplepath <- subway_sample[which(subway_sample$ID=="ID10"),]
samplepath
shortestpath_2(depart = samplepath$up_Name, depart_line = samplepath$up_Line,
             arrival = samplepath$down_Name, arrival_line = samplepath$down_Line)
```


### Find shortestpath in all case(transfer count : 0,1,2)

`shortestpath` will give you information about the shortest path to the subway in all case. 
we can compare these result with shortestpath_2 above.

when we input same path in `shortestpath_2()` and `shortestpath()`, but `shortestpath()` in all case get another path.

because `shortestpath()` will give you totally selected path from another three.

```{r}
shortestpath(depart = samplepath$up_Name, depart_line = samplepath$up_Line,
             arrival = samplepath$down_Name, arrival_line = samplepath$down_Line)
```


### plot map which includes shortestpath info.

`pathplot` will give you a map which includes shortestpath information.

It depends on 'nkmap' packages. i suggest to install nkmap in ["subinjo92"](https://github.com/subinjo92/nkmap) 's github.

```{r, message=FALSE}
library(nkmap)

samplepath <- subway_sample[which(subway_sample$ID=="ID15"),]
samplepath

pathplot(depart = samplepath$up_Name, depart_line = samplepath$up_Line,
             arrival = samplepath$down_Name, arrival_line = samplepath$down_Line, naver_secret, naver_key, kakao_key, zoom =8)

samplepath <- subway_sample[which(subway_sample$ID=="ID30"),]
samplepath

pathplot(depart = samplepath$up_Name, depart_line = samplepath$up_Line,
             arrival = samplepath$down_Name, arrival_line = samplepath$down_Line, naver_secret, naver_key, kakao_key, zoom =7)
```


## Introduction to sub-functions.

* `checkline()` will give you accurate transfer path.

* `get_pathinfo()` will give you total time & count from A->B in same line.

* `get_transfercriteria()` will give you selected case of transfer route through longitude&lattitude. This function will divide the wide space based depart/arrival station.

* `get_transferinfo()` will give you all case of transfer route.
